---
title: "A really not so simple document"
date: 2026-09-17
output:
  html_document: 
    toc: true
    toc_float: true
  pdf_document: default
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble
```{r, echo = FALSE} 
library(tidyverse)
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.05), 
    y = 1 + 2 * x + rnorm(1000)
  )

head(plot_df)
```

# Section 5: Learning Assessment
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

Solution

```{r}
set.seed(0)

data_frame <- 
  tibble(
    numeric_var = rnorm(500, mean = 1),
    logical_vector = case_when(
      numeric_var >= 0 ~ 1,
      numeric_var < 0 ~ 0), 
    log_var = numeric_var > 0,
    numeric_vector = abs(numeric_var)
  )

data_frame |> 
  ggplot() + 
  geom_histogram(mapping = aes(x = numeric_vector))

round(median(data_frame$numeric_vector), digits = 2)

# If eval = FALSE, then the block of code does not run
# If echo = FALSE, then block of code does not appear in R Markdown file 
```

The median is `r round(median(pull(data_frame, numeric_vector)), digits = 2)`  
The median is `r round(median(data_frame$numeric_vector), digits = 2)`  

# Section 6 Formatting 

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The median is `r round(median(data_frame$numeric_vector), digits = 2)`.

* The mean is `r round(mean(data_frame$numeric_vector), digits = 2)`.

* The standard deviation is `r round(sd(data_frame$numeric_vector), digits = 2)`.

This plot shows the distribution of the absolute value. 

What if I try to add a histogram? 

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```



